---
title: "CHEMISTREE – Descriptive Data Overview"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    number-sections: true
    output-dir: ./output/descriptive_overview
params:
  prefer: "wide"     # one of: wide, long, clean_split, clean
  out_dir: "preprocessing/output"  # where CSVs were written by the pipeline
  raw_path: "data/chemestree_jobmatch.csv"
execute:
  echo: true
  message: false
  warning: false
---

```{r}
#| label: setup
suppressPackageStartupMessages({
  library(dplyr); library(readr); library(tidyr); library(stringr)
  library(forcats); library(ggplot2); library(purrr); library(scales)
  library(Matrix); library(DT); library(forcats); library(maps); library(stringi)
})

paths <- list(
  clean       = file.path("../..", params$out_dir, "data_clean.csv"),
  clean_split = file.path("../..", params$out_dir, "data_clean_split.csv"),
  long        = file.path("../..", params$out_dir, "data_long.csv"),
  wide        = file.path("../..", params$out_dir, "data_wide.csv")
)
exist <- vapply(paths, file.exists, logical(1))

prefer <- match.arg(params$prefer, c("wide","long","clean_split","clean"))
order_try <- c(prefer, setdiff(c("wide","long","clean_split","clean"), prefer))
chosen <- NULL
for (nm in order_try) if (exist[[nm]]) { chosen <- nm; break }
if (is.null(chosen)) stop("No dataset found in `", params$out_dir, "`")

# Load selected + others if present
df_main  <- read_csv(paths[[chosen]], show_col_types = FALSE)
df_wide  <- if (exist[["wide"]])  read_csv(paths$wide,  show_col_types = FALSE) else NULL
df_long  <- if (exist[["long"]])  read_csv(paths$long,  show_col_types = FALSE) else NULL
df_clean <- if (exist[["clean"]]) read_csv(paths$clean, show_col_types = FALSE) else NULL
df_clean_split <- if (exist[["clean_split"]]) read_csv(paths$clean_split, show_col_types = FALSE) else NULL

# By design: df_main == df_wide for summaries.
if (!is.null(df_wide)) df_main <- df_wide

# Helpers ------------------------------------------------------------
stopifnot("ID" %in% names(df_main))
cols_all <- setdiff(names(df_main), "ID")

# Name-based family detection (robust to your schema)
ind_cols <- cols_all[grepl(":\\s", cols_all)]          # "Var: Cat(: Subcat)"
sc_cols  <- setdiff(cols_all, ind_cols)                # exactly the variable name (DE/EN & other langs here)

is_indicator <- function(x) is.numeric(x) && all(x %in% c(0, 1, NA), na.rm = TRUE)
shorten_prefix <- function(x) {
  # Normalize NBSP to regular space
  x <- gsub("\u00A0", " ", x, fixed = TRUE)

  str_replace(
    x,
    regex(
      paste0(
        "^(",
          # 1) Fachliches & funktionales Kompetenz(-|–|—)Profil:
          "Fachliches\\s*&\\s*funktionales\\s*Kompetenz[-–—]Profil\\s*:\\s*",
          "|",
          # 2) Wunschbranche:
          "Wunschbranche\\s*:\\s*",
          "|",
          # 3) Sprachkompetenz <LANG> (with flexible spaces, optional colon)
          "Sprachkompetenz\\s+:?\\s*",
        ")"
      ),
      ignore_case = FALSE
    ),
    ""
  )
}


wrap <- function(x, width = 40) str_wrap(x, width = width)

var_order <- c(
  "Wunschbranche","Branchen-/Bereichserfahrung","Favorisierte Unternehmensgröße",
  "Unternehmensumfeld","Einsatzort (Großraum)","Remote-Tätigkeit","Umfang der Stelle",
  "Reisetätigkeit","Sprachkompetenz DEUTSCH","Sprachkompetenz ENGLISCH",
  "WEITERE Sprachkompetenzen","Fachliches & funktionales Kompetenz-Profil",
  "Spezifische/r Themen- und Fachbereich/e","Tätigkeitsfeld","Beschreibung der Aufgabe",
  "Persönliche Kompetenzen","Sozial-kommunikative Kompetenzen",
  "Aktivitäts- und umsetzungsorientierte Kompetenzen",
  "Denke an Deine bisherigen Teamerfahrungen zurück. Welche Rolle(n) nimmst Du in Teams am liebsten ein?",
  "Welche Werte sind Dir in dem Team der zu besetzenden Stelle besonders wichtig?",
  "Mit welchen Aussagen können Unternehmen bei Dir punkten?","Meine Bildungsabschlüsse","Bruttojahresgehalt"
)

# helper: compact label "category — subcategory" (if sub exists)
mk_label <- function(category, subcategory) {
  ifelse(is.na(subcategory) | subcategory == "", category, paste0(category, " — ", subcategory))
}

plot_top_for_variable <- function(df_long, var, top_n = 15) {
  stopifnot(all(c("ID","variable","category","subcategory") %in% names(df_long)))
  
  df_long %>%
    filter(variable == var) %>%
    mutate(label = mk_label(category, subcategory)) %>%
    count(label, sort = TRUE, name = "n") %>%
    slice_head(n = top_n) %>%
    arrange(n) %>%
    ggplot(aes(x = reorder(label, n), y = n)) +
    geom_col() +
    coord_flip() +
    theme_minimal(base_size = 12) +
    labs(title = var, x = NULL, y = "Anzahl")
}

```

## Executive summary

```{r}
#| label: executive-summary
# (keeps your logic; adds clear context + formatting)

n_obs <- nrow(df_main)

top_inds <- df_main %>%
  summarise(across(all_of(ind_cols), ~ sum(. == 1, na.rm = TRUE))) %>%
  pivot_longer(everything(), names_to = "feature", values_to = "n") %>%
  arrange(desc(n)) %>%
  rename(n_ones = n) %>%
  mutate(
    feature = shorten_prefix(feature),
    pct_ones = n_ones / n_obs
  ) %>%
  slice_head(n = 10)

sc_missing <- df_main %>%
  summarise(across(all_of(sc_cols), ~ sum(.x %in% c(NA, "", "keine Angabe")))) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "n_missing") %>%
  mutate(
    variable = shorten_prefix(variable),
    pct_missing = n_missing / n_obs,
    n_nonmissing = n_obs - n_missing
  ) %>%
  select(-n_missing) %>%
  arrange(desc(pct_missing)) %>%
  slice_head(n = 10)

# --- context header -----------------------------------------------------------
cat("### Executive summary\n\n")

# Overview line
overview_tbl <- tibble::tibble(
  dataset       = chosen,
  rows          = n_obs,
  cols          = length(cols_all),
  indicators    = length(ind_cols),
  single_choice = length(sc_cols)
)
print(overview_tbl)

cat("\n**Top indicator features (top 10)** — *Number and share of respondents who selected each feature.*\n\n")

# Nicely formatted top indicators
top_inds_out <- top_inds %>%
  transmute(
    Feature      = feature,
    Selections   = n_ones,
    Share        = scales::percent(pct_ones, accuracy = 0.1)
  )
print(top_inds_out, n = nrow(top_inds_out))

cat("\n**Single-choice variables with most missing/‘keine Angabe’ (top 10)** — *Share of rows with missing/blank/‘keine Angabe’ plus available count.*\n\n")

sc_missing_out <- sc_missing %>%
  transmute(
    Variable         = variable,
    `Missing share`  = scales::percent(pct_missing, accuracy = 0.1),
    `Available (n)`  = n_nonmissing
  )
print(sc_missing_out, n = nrow(sc_missing_out))
```

## Data dictionary

```{r}
#| label: data-dictionary
# Keep your logic; add minimal context, compact preview, and an export.

# family as ordered factor
family_vec <- ifelse(cols_all %in% ind_cols, "indicator", "single-choice/text")
family_fac <- factor(family_vec, levels = c("indicator", "single-choice/text"))

n_obs <- nrow(df_main)

n_unique_vec  <- vapply(df_main[cols_all], function(x) n_distinct(x, na.rm = TRUE), integer(1))
n_nonmiss_vec <- vapply(df_main[cols_all], function(x) sum(!is.na(x)),               integer(1))

# % of ones only for indicators
pct_ones_vec <- vapply(
  cols_all,
  function(col) if (col %in% ind_cols) round(mean(df_main[[col]] == 1, na.rm = TRUE) * 100, 2) else NA_real_,
  numeric(1)
)

# optional: missingness only for single-choice/text (kept but not foregrounded)
sc_missing_vec <- vapply(
  cols_all,
  function(col) if (!(col %in% ind_cols)) sum(df_main[[col]] %in% c(NA, "", "keine Angabe")) else NA_integer_,
  integer(1)
)
sc_pct_missing_vec <- round(100 * sc_missing_vec / n_obs, 1)

dict <- tibble::tibble(
  variable        = cols_all,
  family          = family_fac,
  n_unique        = n_unique_vec,
  n_nonmiss       = n_nonmiss_vec,
  pct_ones        = pct_ones_vec,         # only meaningful for indicators
  sc_pct_missing  = sc_pct_missing_vec    # only meaningful for single-choice/text
) %>%
  arrange(family, desc(n_unique))

# ---- concise context & preview (no repetition of exec summary) ---------------
cat("### Data dictionary\n\n")
cat(paste0(
  "Columns: ", length(cols_all),
  " | Indicators: ", length(ind_cols),
  " | Single-choice/Text: ", length(sc_cols), "\n\n",
  "Preview shows variable name, family, unique values, non-missing count, and (for indicators) % of 1s.\n\n"
))

dict_preview <- dict %>%
  mutate(
    variable = shorten_prefix(variable),
    pct_ones = ifelse(is.na(pct_ones), NA, paste0(pct_ones, "%"))
  ) %>%
  select(variable, family, n_unique, n_nonmiss, pct_ones) %>%
  slice_head(n = 30)

print(dict_preview, n = nrow(dict_preview))

```

## Indicators plot

```{r}
#| label: plot-indicators-top
#| fig.height: 20
#| fig.width: 8
# Uses pct_ones from 'dict' (built in data-dictionary)

stopifnot(exists("dict"))

ind_tab <- dict %>%
  filter(family == "indicator") %>%
  transmute(
    variable_lbl = shorten_prefix(variable),
    pct1 = as.numeric(pct_ones)   # already 0–100 in dict
  ) %>%
  filter(!is.na(pct1)) %>%
  arrange(desc(pct1))

if (nrow(ind_tab)) {
  top_n <- min(30, nrow(ind_tab))
  pdat  <- ind_tab %>%
    slice_head(n = top_n) %>%
    mutate(variable_lbl = str_wrap(variable_lbl, 35) %>% 
                 str_trunc(130)) %>%
    arrange(pct1)

  ggplot(pdat, aes(x = fct_reorder(variable_lbl, pct1), y = pct1)) +
    geom_segment(aes(xend = variable_lbl, y = 0, yend = pct1)) +
    geom_point(size = 2) +
    geom_text(aes(label = paste0(round(pct1, 1), "%")), hjust = -0.2, size = 3) +
    scale_y_continuous(
      name = "Anteil 1er (%)",
      breaks = seq(0, 100, 10),
      limits = c(0, 100),
      expand = expansion(mult = c(0, 0.08)),
      sec.axis = dup_axis(name = "Anteil 1er (%)")
    ) +
    geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
    coord_flip(clip = "off") +
    theme_minimal(base_size = 12) +
    theme(
      plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
      axis.text.y = element_text(lineheight = 0.9, size = 9),
      axis.title.x.top    = element_text(margin = margin(b = 8)),
      axis.ticks.x.top    = element_line(),
      axis.title.x.bottom = element_text(margin = margin(t = 8))
    ) +
    labs(
      title    = "Top Indicator-Features nach Anteil",
      subtitle = paste0("Basis: N = ", format(n_obs, big.mark = ".")),
      x = NULL, y = "Anteil 1er (%)"
    )
} else {
  cat("No indicator columns available to plot.\n")
}
```

## Single-choice distributions (w/o Languages)

```{r}
#| label: single-choice-dists
#| fig.height: 3
#| fig.width: 8
if (length(sc_cols)) {
  show_cols <- c("Reisetätigkeit","Remote-Tätigkeit")

  for (cc in show_cols) {
    if (!cc %in% names(df_main)) next

    tab <- df_main %>%
      filter(!(.data[[cc]] %in% c(NA, "", "keine Angabe"))) %>%
      count(opt = .data[[cc]], name = "n") %>%
      mutate(
        pct = n / sum(n) * 100,
        lbl = as.character(opt) %>% str_wrap(35) %>% str_trunc(80, ellipsis = "...")
      ) %>%
      arrange(pct)

    if (nrow(tab) == 0) next

    p <- ggplot(tab, aes(x = fct_reorder(lbl, pct), y = pct)) +
      geom_segment(aes(xend = lbl, y = 0, yend = pct)) +
      geom_point(size = 2) +
      geom_text(aes(label = paste0(round(pct, 1), "%")), hjust = -0.2, size = 3) +
      scale_y_continuous(
        name = "Anteil (%)",
        breaks = seq(0, 100, 10),
        limits = c(0, 100),
        expand = expansion(mult = c(0, 0.08))
      ) +
      geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
      coord_flip(clip = "off") +
      theme_minimal(base_size = 12) +
      theme(
        plot.margin = grid::unit(c(5.5, 20, 5.5, 5.5), "pt"),
        axis.text.y = element_text(lineheight = 0.9, size = 9)
      ) +
      labs(
        title    = cc,
        x = NULL, y = "Anteil (%)"
      )

    print(p)   
  }
}
```

## Languages

```{r}
#| label: single-choice-missing
if (length(sc_cols)) {
 sc_missing
}
```

```{r}
#| label: sprachkompetenz
# Einzelländer (DE/EN) – Lollipop, Prozent, kurze Labels, keine Top-Achse
short_level <- function(x) case_when(
  str_detect(x, "Elementare Sprachanwendung")    ~ "Elementare Sprachanwendung (A1 / A2)",
  str_detect(x, "Selbstständige Sprachanwendung")~ "Selbstständige Sprachanwendung (B1 / B2)",
  str_detect(x, "Kompetente Sprachverwendung")   ~ "Kompetente Sprachverwendung (C1 / C2)",
  TRUE ~ as.character(x)
)

for (cc in c("Sprachkompetenz DEUTSCH", "Sprachkompetenz ENGLISCH")) {
  if (cc %in% names(df_main)) {
    tab <- df_main %>%
      filter(!(.data[[cc]] %in% c(NA, "", "keine Angabe"))) %>%
      count(opt = .data[[cc]], name = "n") %>%
      mutate(
        level_short = short_level(opt),
        pct = n / sum(n) * 100
      ) %>%
      arrange(pct)

    if (nrow(tab)) {
      p <- ggplot(tab, aes(x = forcats::fct_reorder(level_short, pct), y = pct)) +
        geom_segment(aes(xend = level_short, y = 0, yend = pct)) +
        geom_point(size = 2) +
        geom_text(aes(label = paste0(round(pct, 1), "%")), hjust = -0.2, size = 3) +
        scale_y_continuous(
          name = "Anteil (%)",
          breaks = seq(0, 100, 10),
          limits = c(0, 100),
          expand = expansion(mult = c(0, 0.08))
        ) +
        geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
        coord_flip(clip = "off") +
        theme_minimal(base_size = 12) +
        theme(
          plot.margin = grid::unit(c(5.5, 20, 5.5, 5.5), "pt"),
          axis.text.y = element_text(lineheight = 0.9, size = 9)
        ) +
        labs(
          title    = cc,
          subtitle = "Hinweis: 'keine Angabe' und fehlende/leer Werte sind ausgeschlossen",
          x = NULL, y = "Anteil (%)"
        )
      print(p)
    }
  }
}

# Weitere Sprachen – gestapelt (bleibt)
other_lang_cols <- names(df_main)[
  startsWith(names(df_main), "Sprachkompetenz ") &
  !(names(df_main) %in% c("Sprachkompetenz DEUTSCH","Sprachkompetenz ENGLISCH"))
]
if (length(other_lang_cols)) {
  long_lang <- df_main %>%
    select(all_of(other_lang_cols)) %>%
    pivot_longer(everything(), names_to = "language", values_to = "level") %>%
    filter(!level %in% c(NA, "", "keine Angabe")) %>%
    mutate(
      language  = sub("^Sprachkompetenz\\s+", "", language),
      level_lbl = short_level(level)
    )
  long_lang$level_lbl <- factor(
    long_lang$level_lbl,
    levels = c("Elementare Sprachanwendung (A1 / A2)",
               "Selbstständige Sprachanwendung (B1 / B2)",
               "Kompetente Sprachverwendung (C1 / C2)"),
    ordered = TRUE
  )
  
   # Anteil "keine Angabe" pro weiterer Sprache – Lollipop
  miss_lang <- df_main %>%
    select(all_of(other_lang_cols)) %>%
    pivot_longer(everything(), names_to = "language", values_to = "level") %>%
    mutate(
      language   = sub("^Sprachkompetenz\\s+", "", language),
      is_missing = is.na(level) | level == "" | level == "keine Angabe"
    ) %>%
    group_by(language) %>%
    summarise(
      n_missing   = sum(is_missing),
      n_total     = n(),
      pct_missing = n_missing / n_total * 100,
      .groups = "drop"
    ) %>%
    arrange(pct_missing)

  if (nrow(miss_lang)) {
    p_miss <- ggplot(miss_lang, aes(x = forcats::fct_reorder(language, pct_missing), y = pct_missing)) +
      geom_segment(aes(xend = language, y = 0, yend = pct_missing)) +
      geom_point(size = 2) +
      geom_text(aes(label = paste0(round(pct_missing, 1), "%")), hjust = -0.2, size = 3) +
      scale_y_continuous(
        name = "Anteil fehlend / 'keine Angabe' (%)",
        breaks = seq(0, 100, 10),
        limits = c(0, 100),
        expand = expansion(mult = c(0, 0.08))
      ) +
      geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
      coord_flip(clip = "off") +
      theme_minimal(base_size = 12) +
      theme(
        plot.margin = grid::unit(c(5.5, 20, 5.5, 5.5), "pt"),
        axis.text.y = element_text(lineheight = 0.9, size = 9)
      ) +
      labs(
        title    = "Weitere Sprachkompetenzen – Anteil 'keine Angabe' / keine Kenntnisse",
        x = NULL, y = "Anteil (%)"
      )
    print(p_miss)
  }

  print(
    ggplot(long_lang, aes(x = language, fill = level_lbl)) +
      geom_bar(position = "fill") +
      coord_flip() +
      scale_y_continuous(labels = scales::percent_format()) +
      theme_minimal(base_size = 12) +
      labs(
        title    = "Weitere Sprachkompetenzen (relative Verteilung)",
        subtitle = "Hinweis: 'keine Angabe' ist hier ausgeschlossen",
        x = NULL, y = "Anteil", fill = "Niveau"
      )
  )
}
```

## Fachliches & funktionales Kompetenz-Profil

```{r}
#| label: ffkp
#| fig.height: 12
#| fig.width: 8
ffkp_cols <- names(df_main)[startsWith(names(df_main), "Fachliches & funktionales Kompetenz-Profil")]
if (length(ffkp_cols)) {
  if (all(vapply(df_main[ffkp_cols], is_indicator, logical(1)))) {
    ffkp_counts <- df_main %>%
      summarise(across(all_of(ffkp_cols), ~ sum(. == 1, na.rm = TRUE))) %>%
      pivot_longer(everything(), names_to = "feature", values_to = "n") %>%
      mutate(
        feature_lbl = shorten_prefix(feature) %>% str_wrap(35) %>% str_trunc(80),
        pct = n / n_obs * 100
      ) %>%
      arrange(desc(pct))

    top_n <- min(20, nrow(ffkp_counts))
    pdat  <- ffkp_counts %>% slice_head(n = top_n) %>% arrange(pct)

    ggplot(pdat, aes(x = fct_reorder(feature_lbl, pct), y = pct)) +
      geom_segment(aes(xend = feature_lbl, y = 0, yend = pct)) +
      geom_point(size = 2) +
      geom_text(aes(label = paste0(round(pct, 1), "%")), hjust = -0.2, size = 3) +
      # Achsenformat wie beim Wunschbranchen-Plot + 50%-Linie
      scale_y_continuous(
        name = "Anteil (%)",
        breaks = seq(0, 100, 10),
        limits = c(0, 100),
        expand = expansion(mult = c(0, 0.08)),
        sec.axis = dup_axis(name = "Anteil (%)")
      ) +
      geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
      coord_flip(clip = "off") +
      theme_minimal(base_size = 12) +
      theme(
        plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
        axis.text.y = element_text(lineheight = 0.9, size = 9),
        axis.title.x.top    = element_text(margin = margin(b = 8)),
        axis.ticks.x.top    = element_line(),
        axis.title.x.bottom = element_text(margin = margin(t = 8))
      ) +
      labs(
        title    = "F&f Kompetenz-Profil – Anteil Top-Auswahlen",
        subtitle = paste0("Basis: N = ", format(n_obs, big.mark = ".")),
        x = NULL, y = "Anteil (%)"
      )
  } else {
    long_ffkp <- df_main %>% select(all_of(ffkp_cols)) %>%
      pivot_longer(everything(), names_to = "feature", values_to = "value") %>%
      filter(!value %in% c(NA, "", "keine Angabe")) %>%
      mutate(feature_lbl = shorten_prefix(feature) %>% str_wrap(35) %>% str_trunc(80))
    ggplot(long_ffkp, aes(x = feature_lbl)) +
      geom_bar() +
      coord_flip() +
      theme_minimal(base_size = 12) +
      theme(axis.text.y = element_text(lineheight = 0.9, size = 9)) +
      labs(title = "F&f Kompetenz-Profil – Einträge", x = NULL, y = "Anzahl")
  }
} else {
  cat("No F&f Kompetenz-Profil columns found.\n")
}

```

```{r}
#| label: ffkp_kategorien_only
#| fig.height: 14
#| fig.width: 8
#| warning: false
#| message: false

# Long table selector
long_src <- if (exists("df_long")) df_long else if (exists("df_main")) df_main else NULL
stopifnot(!is.null(long_src), all(c("ID","variable","category","subcategory") %in% names(long_src)))

var    <- "Fachliches & funktionales Kompetenz-Profil"
n_obs  <- dplyr::n_distinct(long_src$ID)

ffkp <- long_src %>%
  dplyr::filter(variable == var) %>%
  dplyr::mutate(
    cat = stringr::str_squish(category)
  ) %>%
  dplyr::filter(!is.na(cat) & cat != "") %>%
  dplyr::distinct(ID, cat) %>%                     # one hit per Person × Kategorie
  dplyr::count(cat, name = "n_cat", sort = TRUE) %>%
  dplyr::mutate(
    pct     = 100 * n_cat / n_obs,
    cat_lbl = stringr::str_wrap(cat, 40)
  ) %>%
  dplyr::arrange(pct)

ggplot(ffkp, aes(x = forcats::fct_reorder(cat_lbl, pct), y = pct)) +
  geom_segment(aes(xend = cat_lbl, y = 0, yend = pct)) +
  geom_point(size = 2) +
  geom_text(aes(label = paste0(round(pct, 1), "%")),
            hjust = -0.2, size = 3) +
  scale_y_continuous(
    name   = "Anteil (%)",
    limits = c(0, 100),
    breaks = seq(0, 100, 10),
    expand = expansion(mult = c(0, 0.08)),
    sec.axis = dup_axis(name = "Anteil (%)")
  ) +
  geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
  coord_flip(clip = "off") +
  theme_minimal(base_size = 12) +
  theme(
    plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
    axis.text.y = element_text(lineheight = 0.9, size = 9),
    axis.title.x.top    = element_text(margin = margin(b = 8)),
    axis.ticks.x.top    = element_line(),
    axis.title.x.bottom = element_text(margin = margin(t = 8))
  ) +
  labs(
    title    = "F&f Kompetenz-Profil – Kategorien (Anteil an allen Befragten)",
    subtitle = paste0("Basis: N = ", format(n_obs, big.mark = ".")),
    x = NULL, y = "Anteil (%)"
  )

```

```{r}
#| label: ffkp_subcats_overall
#| warning: false
#| message: false

# Long table selector
long_src <- if (exists("df_long")) df_long else if (exists("df_main")) df_main else NULL
stopifnot(!is.null(long_src), all(c("ID","variable","category","subcategory") %in% names(long_src)))

var    <- "Fachliches & funktionales Kompetenz-Profil"
n_obs  <- dplyr::n_distinct(long_src$ID)

# Subkategorien gesamt: Anteil an allen Befragten (lollipop)
ffkp_sub <- long_src %>%
  dplyr::filter(variable == var) %>%
  dplyr::mutate(sub = dplyr::if_else(is.na(subcategory) | subcategory == "",
                                     NA_character_, stringr::str_squish(subcategory))) %>%
  dplyr::filter(!is.na(sub) & sub != "") %>%
  dplyr::distinct(ID, sub) %>%                # Person zählt höchstens 1× pro Subkategorie
  dplyr::count(sub, name = "n_sub", sort = TRUE) %>%
  dplyr::mutate(
    pct     = 100 * n_sub / n_obs,
    sub_lbl = stringr::str_wrap(sub, 40)
  ) %>%
  dplyr::arrange(pct)

ggplot(ffkp_sub, aes(x = forcats::fct_reorder(sub_lbl, pct), y = pct)) +
  geom_segment(aes(xend = sub_lbl, y = 0, yend = pct)) +
  geom_point(size = 2) +
  geom_text(aes(label = paste0(round(pct, 1), "%")),
            hjust = -0.2, size = 3) +
  scale_y_continuous(
    name   = "Anteil (%)",
    limits = c(0, 100),
    breaks = seq(0, 100, 10),
    expand = expansion(mult = c(0, 0.08))
  ) +
  geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
  coord_flip(clip = "off") +
  theme_minimal(base_size = 12) +
  theme(
    plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
    axis.text.y = element_text(lineheight = 0.9, size = 9),
    axis.title.x.top    = element_text(margin = margin(b = 8)),
    axis.ticks.x.top    = element_line()
  ) +
  labs(
    title    = "F&f Kompetenz-Profil – Subkategorien (Anteil an allen Befragten)",
    subtitle = paste0("Basis: N = ", format(n_obs, big.mark = ".")),
    x = NULL, y = "Anteil (%)"
  )
```

```{r}
#| label: ffkp_topk_stacked_subcats_fix
#| fig.height: 8
#| fig.width: 10
#| warning: false
#| message: false

long_src <- if (exists("df_long")) df_long else if (exists("df_main")) df_main else NULL
stopifnot(!is.null(long_src), all(c("ID","variable","category","subcategory") %in% names(long_src)))

var    <- "Fachliches & funktionales Kompetenz-Profil"
n_obs  <- dplyr::n_distinct(long_src$ID)
top_k  <- 10

# Top categories by share (based on ALL who picked the category)
ffkp_cats <- long_src %>%
  dplyr::filter(variable == var) %>%
  dplyr::mutate(cat = stringr::str_squish(category)) %>%
  dplyr::filter(!is.na(cat) & cat != "") %>%
  dplyr::distinct(ID, cat) %>%
  dplyr::count(cat, name = "n_cat", sort = TRUE) %>%
  dplyr::mutate(pct = 100 * n_cat / n_obs)

top_cats <- ffkp_cats %>%
  dplyr::slice_head(n = min(top_k, nrow(ffkp_cats))) %>%
  dplyr::pull(cat)

# Build subcategory mix INCLUDING an "(ohne Angabe)" bucket
ffkp_sub_share <- long_src %>%
  dplyr::filter(variable == var) %>%
  dplyr::mutate(
    cat = stringr::str_squish(category),
    sub = stringr::str_squish(subcategory),
    sub2 = dplyr::if_else(is.na(sub) | sub == "", "(ohne Angabe)", sub)
  ) %>%
  dplyr::filter(!is.na(cat) & cat %in% top_cats) %>%
  dplyr::distinct(ID, cat, sub2) %>%                    # one vote per Person × Cat × Sub
  dplyr::count(cat, sub2, name = "n_cat_sub") %>%
  dplyr::group_by(cat) %>%
  dplyr::mutate(
    base_n    = sum(n_cat_sub),                         # ALL selections for this category (incl. ohne Angabe)
    pct_in_cat = 100 * n_cat_sub / base_n
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    cat_lbl = stringr::str_wrap(cat, 25),
    sub_lbl = stringr::str_wrap(sub2, 30)
  )

# keep category order like the top list (descending by overall share)
cat_order <- ffkp_cats %>%
  dplyr::filter(cat %in% top_cats) %>%
  dplyr::arrange(dplyr::desc(pct)) %>%
  dplyr::pull(cat)

ffkp_sub_share <- ffkp_sub_share %>%
  dplyr::mutate(cat_lbl = factor(cat_lbl, levels = stringr::str_wrap(cat_order, 25)))


ggplot(ffkp_sub_share, aes(x = cat_lbl, y = n_cat_sub, fill = sub_lbl)) +
  geom_col(width = 0.85, position = "fill") +        # <- normalize per category
  scale_y_continuous(
    name   = "Anteil je Kategorie (%)",
    labels = scales::percent_format(accuracy = 1),
    breaks = seq(0, 1, 0.1),
    expand = expansion(mult = 0, add = 0)
  ) +
  coord_flip(clip = "off") +
  guides(fill = guide_legend(title = "Subkategorie", ncol = 1)) +
  theme_minimal(base_size = 12) +
  theme(axis.text.y = element_text(lineheight = 0.9, size = 9)) +
  labs(
    title    = "F&f Kompetenz-Profil – Subkategorien in den Top-K Kategorien",
    subtitle = "Bars sind je Kategorie normiert (sum = 100%)",
    x = NULL, y = "Anteil je Kategorie (%)"
  )



```

## Wunschbranchen

```{r}
#| label: wunschbranche
#| fig.height: 12
#| fig.width: 8
wb_cols <- grep("^Wunschbranche", names(df_main), value = TRUE)

if (length(wb_cols) && all(vapply(df_main[wb_cols], is_indicator, logical(1)))) {
  wb_counts <- df_main %>%
    summarise(across(all_of(wb_cols), ~ sum(. == 1, na.rm = TRUE))) %>%
    pivot_longer(everything(), names_to = "Wunschbranche", values_to = "n") %>%
    mutate(
      pct    = n / n_obs,
      WB_lbl = sub("^Wunschbranche:\\s*", "", Wunschbranche, perl = TRUE) |>
                 str_wrap(35) |>
                 str_trunc(80)
    ) %>%
    arrange(desc(pct))

  top_n <- min(25, nrow(wb_counts))
  pdat  <- wb_counts %>% slice_head(n = top_n) %>% arrange(pct)

  ggplot(pdat, aes(x = fct_reorder(WB_lbl, pct), y = pct)) +
    geom_segment(aes(xend = WB_lbl, y = 0, yend = pct)) +
    geom_point(size = 2) +
    geom_text(aes(label = scales::percent(pct, accuracy = 0.1)),
              hjust = -0.2, size = 3) +
    geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 0.4, color = "grey50") +
    coord_flip(clip = "off") +
    scale_y_continuous(
      labels  = scales::percent_format(),
      limits  = c(0, 1),
      expand  = expansion(mult = c(0, 0.08)),
      sec.axis = dup_axis(name = "Anteil (%)")
    ) +
    theme_minimal(base_size = 12) +
    theme(
      plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
      axis.text.y = element_text(lineheight = 0.9, size = 9),
      axis.title.x.top    = element_text(margin = margin(b = 8)),
      axis.ticks.x.top    = element_line(),
      axis.title.x.bottom = element_text(margin = margin(t = 8))
    ) +
    labs(
      title    = "Wunschbranchen – Anteil",
      subtitle = paste0("Basis: N = ", format(n_obs, big.mark = ".")),
      x = NULL, y = "Anteil (%)"
    )
} else {
  cat("No `Wunschbranche` indicator columns found or they are not 0/1.\n")
}
```

## Brachen-/Bereichserfahrung

```{r}
#| label: branchen_bereichserfahrung
#| fig.height: 10
#| fig.width: 8

# Prefer the explicit long table if loaded; otherwise fall back to df_main if it is long-shaped
long_src <- if (!is.null(df_long)) {
  df_long
} else if (all(c("ID","variable","category","subcategory") %in% names(df_main))) {
  df_main
} else {
  NULL
}

if (is.null(long_src)) {
  cat("No long-format table available (need columns: ID, variable, category, subcategory).")
} else {
  target_var <- "Branchen-/Bereichserfahrung"
  
  # # of respondents with any entry for this variable (percentage denominator)
  n_obs <- long_src %>%
    filter(variable == target_var) %>%
    summarise(n_id = n_distinct(ID)) %>%
    pull(n_id)
  
  # Count per CATEGORY only (ignore subcategory)
  branchen_counts <- long_src %>%
    filter(variable == target_var,
                  !is.na(category), category != "") %>%
    count(category, name = "n", sort = TRUE) %>%
    mutate(
      pct = n / n_obs * 100,
      category_lbl = stringr::str_wrap(category, 35) %>% stringr::str_trunc(80)
    )
  
  top_n <- min(20, nrow(branchen_counts))
  pdat  <- branchen_counts %>% slice_head(n = top_n) %>% arrange(pct)
  
  ggplot2::ggplot(pdat, ggplot2::aes(x = forcats::fct_reorder(category_lbl, pct), y = pct)) +
    ggplot2::geom_segment(ggplot2::aes(xend = category_lbl, y = 0, yend = pct)) +
    ggplot2::geom_point(size = 2) +
    ggplot2::geom_text(ggplot2::aes(label = paste0(round(pct, 1), "%")),
                       hjust = -0.2, size = 3) +
    ggplot2::scale_y_continuous(
      name    = "Anteil (%)",
      breaks  = seq(0, 100, 10),
      limits  = c(0, 100),
      expand  = ggplot2::expansion(mult = c(0, 0.08)),
      sec.axis = ggplot2::dup_axis(name = "Anteil (%)")
    ) +
    ggplot2::geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
    ggplot2::coord_flip(clip = "off") +
    ggplot2::theme_minimal(base_size = 12) +
    ggplot2::theme(
      plot.margin          = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
      axis.text.y          = ggplot2::element_text(lineheight = 0.9, size = 9),
      axis.title.x.top     = ggplot2::element_text(margin = ggplot2::margin(b = 8)),
      axis.ticks.x.top     = ggplot2::element_line(),
      axis.title.x.bottom  = ggplot2::element_text(margin = ggplot2::margin(t = 8))
    ) +
    ggplot2::labs(
      title    = "Branchen- / Bereichserfahrung – Anteil Top-Auswahlen",
      subtitle = paste0("Basis: N = ", format(n_obs, big.mark = ".")),
      x = NULL, y = "Anteil (%)"
    )
}

```

## **Favorisierte Unternehmensgröße**

```{r}
#| label: favorisierte_unternehmensgroesse

# Prefer explicit long table if available
long_src <- if (!is.null(df_long)) {
  df_long
} else if (all(c("ID","variable","category","subcategory") %in% names(df_main))) {
  df_main
} else {
  NULL
}

if (is.null(long_src)) {
  cat("No long-format table available (need columns: ID, variable, category, subcategory).")
} else {
  target_var <- "Favorisierte Unternehmensgröße"
  
  # Respondents with any entry for this variable (denominator for %)
  n_obs <- long_src %>%
    filter(variable == target_var) %>%
    summarise(n_id = n_distinct(ID)) %>%
    pull(n_id)
  
  # -------------------------
  # (A) Category-only shares
  # -------------------------
  cat_counts <- long_src %>%
    filter(variable == target_var,
                  !is.na(category), category != "") %>%
    count(category, name = "n", sort = TRUE) %>%
    mutate(
      pct = n / n_obs * 100,
      category_lbl = stringr::str_wrap(category, 35) |> stringr::str_trunc(80)
    )
  
  top_n_cat <- min(15, nrow(cat_counts))
  pdat_cat  <- cat_counts %>% slice_head(n = top_n_cat) %>% arrange(pct)
  
  p_cat <- ggplot2::ggplot(pdat_cat,
                           ggplot2::aes(x = forcats::fct_reorder(category_lbl, pct), y = pct)) +
    ggplot2::geom_segment(ggplot2::aes(xend = category_lbl, y = 0, yend = pct)) +
    ggplot2::geom_point(size = 2) +
    ggplot2::geom_text(ggplot2::aes(label = paste0(round(pct, 1), "%")),
                       hjust = -0.2, size = 3) +
    ggplot2::scale_y_continuous(
      name    = "Anteil (%)",
      breaks  = seq(0, 100, 10),
      limits  = c(0, 100),
      expand  = ggplot2::expansion(mult = c(0, 0.08)),
      sec.axis = ggplot2::dup_axis(name = "Anteil (%)")
    ) +
    ggplot2::geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
    ggplot2::coord_flip(clip = "off") +
    ggplot2::theme_minimal(base_size = 12) +
    ggplot2::theme(
      plot.margin          = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
      axis.text.y          = ggplot2::element_text(lineheight = 0.9, size = 9),
      axis.title.x.top     = ggplot2::element_text(margin = ggplot2::margin(b = 8)),
      axis.ticks.x.top     = ggplot2::element_line(),
      axis.title.x.bottom  = ggplot2::element_text(margin = ggplot2::margin(t = 8))
    ) +
    ggplot2::labs(
      title    = "Favorisierte Unternehmensgröße – Anteil (nur Kategorien)",
      subtitle = paste0("Basis: N = ", format(n_obs, big.mark = ".")),
      x = NULL, y = "Anteil (%)"
    )
  
  print(p_cat)
  
  # ----------------------------------------------
  # (B) Drill-down: show subcategories per category
  #     (keeps top categories; stacks by subcategory)
  # ----------------------------------------------
  # Keep top K categories overall (by count) for readability
  keep_cats <- cat_counts %>%
    slice_head(n = 8) %>%
    pull(category)
  
  sub_counts <- long_src %>%
    filter(variable == target_var,
                  !is.na(category), category != "",
                  category %in% keep_cats) %>%
    mutate(sub = if_else(is.na(subcategory) | subcategory == "",
                                       "(ohne Schwelle)", subcategory)) %>%
    count(category, sub, name = "n", sort = TRUE)
  
  if (nrow(sub_counts) > 0) {
    p_sub <- ggplot2::ggplot(sub_counts,
                             ggplot2::aes(x = forcats::fct_reorder(category, n, sum),
                                          y = n, fill = sub)) +
      ggplot2::geom_col() +
      ggplot2::coord_flip() +
      ggplot2::theme_minimal(base_size = 12) +
      ggplot2::labs(
        title = "Favorisierte Unternehmensgröße – Verteilung Subkategorien (Top-Kategorien)",
        x = NULL, y = "Anzahl", fill = "Subkategorie"
      )
    print(p_sub)
  } else {
    cat("\n(No subcategories present for the kept categories — skipped drill-down plot.)\n")
  }
}
```

## Unternehmensumfeld

```{r}
#| label: unternehmensumfeld

# Prefer explicit long table if available
long_src <- if (!is.null(df_long)) {
  df_long
} else if (all(c("ID","variable","category","subcategory") %in% names(df_main))) {
  df_main
} else {
  NULL
}

if (is.null(long_src)) {
  cat("No long-format table available (need columns: ID, variable, category, subcategory).")
} else {
  target_var <- "Unternehmensumfeld"
  
  # Respondents with any entry for this variable (denominator for %)
  n_obs <- long_src %>%
    filter(variable == target_var) %>%
    summarise(n_id = n_distinct(ID)) %>%
    pull(n_id)
  
  # Count per CATEGORY only
  env_counts <- long_src %>%
    filter(variable == target_var,
                  !is.na(category), category != "") %>%
    count(category, name = "n", sort = TRUE) %>%
    mutate(
      pct = n / n_obs * 100,
      category_lbl = stringr::str_wrap(category, 35) |> stringr::str_trunc(80)
    )
  
  top_n <- min(20, nrow(env_counts))
  pdat  <- env_counts %>% slice_head(n = top_n) %>% arrange(pct)
  
  ggplot2::ggplot(pdat,
                  ggplot2::aes(x = forcats::fct_reorder(category_lbl, pct), y = pct)) +
    ggplot2::geom_segment(ggplot2::aes(xend = category_lbl, y = 0, yend = pct)) +
    ggplot2::geom_point(size = 2) +
    ggplot2::geom_text(ggplot2::aes(label = paste0(round(pct, 1), "%")),
                       hjust = -0.2, size = 3) +
    ggplot2::scale_y_continuous(
      name    = "Anteil (%)",
      breaks  = seq(0, 100, 10),
      limits  = c(0, 100),
      expand  = ggplot2::expansion(mult = c(0, 0.08)),
      sec.axis = ggplot2::dup_axis(name = "Anteil (%)")
    ) +
    ggplot2::geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
    ggplot2::coord_flip(clip = "off") +
    ggplot2::theme_minimal(base_size = 12) +
    ggplot2::theme(
      plot.margin          = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
      axis.text.y          = ggplot2::element_text(lineheight = 0.9, size = 9),
      axis.title.x.top     = ggplot2::element_text(margin = ggplot2::margin(b = 8)),
      axis.ticks.x.top     = ggplot2::element_line(),
      axis.title.x.bottom  = ggplot2::element_text(margin = ggplot2::margin(t = 8))
    ) +
    ggplot2::labs(
      title    = "Unternehmensumfeld – Anteil (Kategorien)",
      subtitle = paste0("Basis: N = ", format(n_obs, big.mark = ".")),
      x = NULL, y = "Anteil (%)"
    )
}

```

## Einsatzort (Großraum)

```{r}
#| label: einsatzort_grossraum_pct
#| fig.height: 10
#| fig.width: 14

suppressPackageStartupMessages({
  library(dplyr); library(tidyr); library(stringr)
  library(forcats); library(ggplot2)
})

# Choose long source
long_src <- if (exists("df_long") && !is.null(df_long)) {
  df_long
} else if (exists("df_main") && all(c("ID","variable","category","subcategory") %in% names(df_main))) {
  df_main
} else {
  NULL
}

if (is.null(long_src)) {

  cat("No long-format table available (need columns: ID, variable, category, subcategory).")

} else {

  # Percent base = ALL respondents in the dataset
  n_obs <- n_distinct(long_src$ID)

  var <- "Einsatzort (Großraum)"
  non_de_groups <- c("Europa außer Deutschland", "USA", "Übrige Welt")
  citystates <- c("Berlin","Hamburg","Bremen")

  dat <- long_src %>%
    filter(variable == var) %>%
    mutate(
      cat = stringr::str_squish(category),
      sub = if_else(is.na(subcategory) | subcategory == "", NA_character_, stringr::str_squish(subcategory))
    )

  # -----------------------------
  # A) Deutschland: Bundesland × Stadt (facettiert, lollipop, % of n_obs)
  # -----------------------------
  de_dat <- dat %>%
    filter(!is.na(cat), !(cat %in% non_de_groups)) %>%
    mutate(
      bundesland = cat,
      city = case_when(
        bundesland %in% citystates ~ bundesland,           # city-state → city = state
        is.na(sub) ~ "(ohne Stadtangabe)",
        TRUE ~ sub
      )
    )

  state_totals <- de_dat %>% count(bundesland, name = "n_state", sort = TRUE)
  keep_states  <- state_totals %>% slice_head(n = min(12L, nrow(state_totals))) %>% pull(bundesland)

  de_top <- de_dat %>%
    filter(bundesland %in% keep_states) %>%
    count(bundesland, city, name = "n", sort = TRUE) %>%
    mutate(pct = n / n_obs * 100) %>%
    group_by(bundesland) %>%
    slice_max(order_by = pct, n = 10, with_ties = FALSE) %>%
    ungroup() %>%
    group_by(bundesland) %>%
    mutate(city = fct_reorder(city, pct)) %>%
    ungroup()

  p_de <- ggplot(de_top, aes(x = city, y = pct)) +
    geom_segment(aes(xend = city, y = 0, yend = pct)) +
    geom_point(size = 2) +
    geom_text(aes(label = paste0(round(pct, 1), "%")),
              hjust = -0.2, size = 3) +
    scale_y_continuous(
      name    = "Anteil (%) an allen Befragten",
      limits  = c(0, 100),
      breaks  = seq(0, 100, 10),
      expand  = expansion(mult = c(0, 0.08)),
      sec.axis = dup_axis(name = "Anteil (%)")
    ) +
    coord_flip(clip = "off") +
    facet_wrap(~ bundesland, scales = "free_y", ncol = 3) +
    theme_minimal(base_size = 12) +
    theme(
      plot.margin          = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
      axis.text.y          = element_text(lineheight = 0.9, size = 9),
      axis.title.x.top     = element_text(margin = margin(b = 8)),
      axis.ticks.x.top     = element_line(),
      axis.title.x.bottom  = element_text(margin = margin(t = 8))
    ) +
    labs(
      title    = "Einsatzort (Großraum) – Deutschland (Top-Städte je Bundesland)",
      subtitle = paste0("Prozentbasis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
      x = NULL, y = "Anteil (%)"
    )
  print(p_de)

  # -----------------------------
  # B) Außerhalb Deutschlands: Gruppe × Region (facettiert, lollipop, % of n_obs)
  # -----------------------------
  non_de <- dat %>%
    filter(!is.na(cat), cat %in% non_de_groups) %>%
    mutate(
      region_group = cat,
      region = if_else(is.na(sub), "(ohne Regionsangabe)", sub)
    )

  if (nrow(non_de) > 0) {

    non_de_top <- non_de %>%
      count(region_group, region, name = "n", sort = TRUE) %>%
      mutate(pct = n / n_obs * 100) %>%
      group_by(region_group) %>%
      slice_max(order_by = pct, n = 15, with_ties = FALSE) %>%
      mutate(region = fct_reorder(region, pct)) %>%
      ungroup()

    p_non_de <- ggplot(non_de_top, aes(x = region, y = pct)) +
      geom_segment(aes(xend = region, y = 0, yend = pct)) +
      geom_point(size = 2) +
      geom_text(aes(label = paste0(round(pct, 1), "%")),
                hjust = -0.2, size = 3) +
      scale_y_continuous(
        name    = "Anteil (%) an allen Befragten",
        limits  = c(0, 100),
        breaks  = seq(0, 100, 10),
        expand  = expansion(mult = c(0, 0.08)),
        sec.axis = dup_axis(name = "Anteil (%)")
      ) +
      coord_flip(clip = "off") +
      facet_wrap(~ region_group, scales = "free_y") +
      theme_minimal(base_size = 12) +
      theme(
        plot.margin          = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
        axis.text.y          = element_text(lineheight = 0.9, size = 9)
      ) +
      labs(
        title    = "Einsatzort (Großraum) – Außerhalb Deutschlands (Top-Regionen je Gruppe)",
        subtitle = paste0("Prozentbasis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
        x = NULL, y = "Anteil (%)"
      )
    print(p_non_de)
  } else {
    cat("\nNo non-Germany entries found for 'Einsatzort (Großraum)'.\n")
  }

  # -----------------------------
  # C) Kompakte Gesamtsicht (Top 30, lollipop, % of n_obs)
  # -----------------------------
  overall <- bind_rows(
    de_dat %>%
      mutate(label = if_else(
        bundesland %in% citystates,
        bundesland,
        paste0(bundesland, " — ", if_else(is.na(sub), bundesland, sub))
      )),
    non_de %>%
      mutate(label = paste0(region_group, " — ", region))
  ) %>%
    filter(!is.na(label), label != "") %>%
    count(label, name = "n", sort = TRUE) %>%
    mutate(pct = n / n_obs * 100) %>%
    slice_head(n = 30) %>%
    arrange(pct)

  p_all <- ggplot(overall, aes(x = reorder(label, pct), y = pct)) +
    geom_segment(aes(xend = label, y = 0, yend = pct)) +
    geom_point(size = 2) +
    geom_text(aes(label = paste0(round(pct, 1), "%")),
              hjust = -0.2, size = 3) +
    scale_y_continuous(
      name    = "Anteil (%) an allen Befragten",
      limits  = c(0, 100),
      breaks  = seq(0, 100, 10),
      expand  = expansion(mult = c(0, 0.08)),
      sec.axis = dup_axis(name = "Anteil (%)")
    ) +
    coord_flip(clip = "off") +
    theme_minimal(base_size = 12) +
    theme(
      plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
      axis.text.y = element_text(lineheight = 0.9, size = 9)
    ) +
    labs(
      title    = "Einsatzort (Großraum) – Top 30 Gesamt (Anteil an allen Befragten)",
      subtitle = paste0("Prozentbasis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
      x = NULL, y = "Anteil (%)"
    )
  print(p_all)

}

```

```{r}
#| label: einsatzort_bundesland_map_fixed_flip
#| fig.height: 7
#| fig.width: 10
#| warning: false
#| message: false

suppressPackageStartupMessages({
  library(dplyr); library(stringr); library(ggplot2)
  library(forcats); library(stringi); library(maps)
})

# pick long table
long_src <- if (exists("df_long")) df_long else if (exists("df_main")) df_main else NULL
stopifnot(!is.null(long_src), all(c("ID","variable","category","subcategory") %in% names(long_src)))

var             <- "Einsatzort (Großraum)"
non_de_groups   <- c("Europa außer Deutschland","USA","Übrige Welt")
non_state_extra <- c("Bundesweit","Ausschließlich remote")
citystates      <- c("Berlin","Hamburg","Bremen")
n_obs           <- n_distinct(long_src$ID)

keyfy <- function(s) stringi::stri_trans_general(s, "Latin-ASCII") |>
  tolower() |> stringr::str_replace_all("[^a-z0-9]+","")

dat <- long_src %>%
  filter(variable == var) %>%
  mutate(
    cat = str_squish(category),
    sub = if_else(is.na(subcategory) | subcategory == "", NA_character_, str_squish(subcategory))
  )

# ---------------- Bundesländer (dedupe respondent × state) --------------------
de_dat <- dat %>%
  filter(!is.na(cat), !(cat %in% c(non_de_groups, non_state_extra))) %>%
  mutate(
    bundesland = cat,
    city = case_when(
      bundesland %in% citystates ~ bundesland,
      is.na(sub)                 ~ "(ohne Stadtangabe)",
      TRUE                       ~ sub
    )
  )

de_state <- de_dat %>%
  distinct(ID, bundesland) %>%
  count(bundesland, name = "n_state", sort = TRUE) %>%
  mutate(pct = 100 * n_state / n_obs,
         key_de = keyfy(bundesland))

have_gisco <- requireNamespace("giscoR", quietly = TRUE) &&
              requireNamespace("sf", quietly = TRUE)

if (have_gisco) {
  suppressPackageStartupMessages({ library(sf) })
  de_sf <- giscoR::gisco_get_nuts(country = "DE", nuts_level = 1, year = 2021) %>%
    mutate(key_gisco = keyfy(NAME_LATN)) %>%
    select(key_gisco, NAME_LATN, geometry)

  de_join <- de_sf %>% left_join(de_state, by = c("key_gisco" = "key_de"))

  # FLIPPED scale: low = dark, high = light
  p_choro <- ggplot(de_join) +
    geom_sf(aes(fill = pct), color = "grey65", linewidth = 0.2) +
    scale_fill_gradient(
      name   = "Anteil (%) an allen Befragten",
      limits = c(0, 100), breaks = seq(0, 100, 10),
      low = "#dbe9f6", high = "#274c77", na.value = "grey90"
    ) +
    coord_sf() +
    theme_minimal(base_size = 12) +
    labs(
      title    = "Einsatzort (Großraum) – Anteil je Bundesland",
      subtitle = paste0("Prozentbasis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
      x = NULL, y = NULL
    )
  print(p_choro)
} else {
  message("giscoR/sf not available → using tile grid fallback.")
  grid_de <- tibble::tribble(
    ~bundesland,                ~abbr, ~x, ~y,
    "Schleswig-Holstein","SH",6,8, "Hamburg","HH",6,9, "Mecklenburg-Vorpommern","MV",7,8,
    "Niedersachsen","NI",5,7, "Bremen","HB",4,8, "Brandenburg","BB",8,7, "Berlin","BE",8,8,
    "Nordrhein-Westfalen","NW",4,6, "Sachsen-Anhalt","ST",7,6, "Sachsen","SN",8,5,
    "Hessen","HE",5,5, "Thüringen","TH",7,5, "Rheinland-Pfalz","RP",4,4, "Saarland","SL",3,4,
    "Baden-Württemberg","BW",5,3, "Bayern","BY",6,3
  )
  state_grid <- grid_de %>% left_join(de_state, by = "bundesland") %>%
    mutate(pct = tidyr::replace_na(pct, 0), pct_lab = if_else(pct > 0, paste0(round(pct, 1), "%"), ""))

  p_tiles <- ggplot(state_grid, aes(x = x, y = y)) +
    geom_tile(aes(fill = pct), width = 0.9, height = 0.9, color = "grey70") +
    geom_text(aes(label = abbr), fontface = "bold", size = 4, color = "white") +
    geom_text(aes(label = pct_lab), nudge_y = -0.35, size = 3.1, color = "white") +
    scale_fill_gradient(low = "#dbe9f6", high = "#274c77",
                        limits = c(0, 100), name = "Anteil (%)") +
    coord_equal() + theme_minimal(base_size = 12) + theme(panel.grid = element_blank()) +
    labs(
      title    = "Einsatzort (Großraum) – Anteil je Bundesland (Tile Grid)",
      subtitle = paste0("Prozentbasis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
      x = NULL, y = NULL
    )
  print(p_tiles)
}

# ---------------- Cities (dedupe respondent × city) ---------------------------
# alias map: German → English names used in maps::world.cities
alias_map <- c(
  "munchen" = "munich",
  "koln" = "cologne",
  "nurnberg" = "nuremberg",
  "hannover" = "hanover",
  "monchengladbach" = "monchengladbach",
  "dusseldorf" = "dusseldorf",   # sometimes "duesseldorf" → dusseldorf after keyfy
  "munster" = "munster",
  "wurzburg" = "wurzburg",
  "koblenz" = "koblenz",
  "braunschweig" = "brunswick",  # world.cities uses Brunswick
  "freiburgimbreisgau" = "freiburg",
  "furth" = "furth",             # keep equal to help typos
  "oberhausen" = "oberhausen",
  "mulheimanderuhr" = "mulheiman der ruhr", # best-effort; world.cities uses "Mulheim"
  "saintaugustin" = "sankt augustin"        # example; extend if needed
)

de_city <- de_dat %>%
  filter(!(city %in% c("(ohne Stadtangabe)"))) %>%
  distinct(ID, city) %>%
  count(city, name = "n_city", sort = TRUE) %>%
  mutate(
    pct       = 100 * n_city / n_obs,
    city_key  = keyfy(city),
    match_key = recode(city_key, !!!alias_map, .default = city_key)
  )

data("world.cities", package = "maps")
cities_de <- world.cities %>%
  as_tibble() %>%
  filter(country.etc == "Germany") %>%
  transmute(
    name, lat = lat, lon = long,
    name_key = keyfy(name)
  )

de_city_xy <- de_city %>%
  left_join(cities_de, by = c("match_key" = "name_key"))

# quick report for unmatched top cities
unmatched <- de_city_xy %>%
  filter(is.na(lat) | is.na(lon)) %>%
  slice_head(n = 15) %>%
  transmute(city, hint = paste0("Add alias: \"", keyfy(city), "\" = \"", keyfy(city), "\""))
if (nrow(unmatched)) {
  message("Unmatched city names (top 15):\n", paste0(" - ", unmatched$city, collapse = "\n"))
}

germany_poly <- ggplot2::map_data("world") %>% filter(region == "Germany")

p_city <- ggplot() +
  geom_polygon(data = germany_poly,
               aes(x = long, y = lat, group = group),
               fill = "grey95", color = "grey60", linewidth = 0.3) +
  geom_point(data = de_city_xy %>% filter(!is.na(lat) & !is.na(lon)),
             aes(x = lon, y = lat, size = pct),
             alpha = 0.65) +
  scale_size_continuous(name = "Anteil (%) an allen Befragten", range = c(1.5, 12)) +
  coord_quickmap() +
  theme_minimal(base_size = 12) +
  labs(
    title    = "Einsatzort (Großraum) – Städte (ein Eintrag pro Person & Stadt)",
    subtitle = paste0("Größe ∝ Anteil (%) · Basis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
    x = NULL, y = NULL
  )
print(p_city)

```

## Umfang der Stelle

```{r}
#| label: umfang_der_stelle
#| fig.height: 4
#| fig.width: 8
#| warning: false
#| message: false

# pick long table (expects: ID, variable, category, subcategory)
long_src <- if (exists("df_long")) df_long else if (exists("df_main")) df_main else NULL
stopifnot(!is.null(long_src), all(c("ID","variable","category") %in% names(long_src)))

var   <- "Umfang der Stelle"
n_obs <- n_distinct(long_src$ID)

dat <- long_src %>%
  filter(variable == var) %>%
  mutate(cat = stringr::str_squish(category)) %>%
  filter(!is.na(cat) & cat != "") %>%
  distinct(ID, cat) %>%                 # max 1 hit per Person × Kategorie
  count(cat, name = "n_cat", sort = TRUE) %>%
  mutate(
    pct     = 100 * n_cat / n_obs,
    cat_lbl = stringr::str_wrap(cat, 40)
  ) %>%
  arrange(pct)

ggplot(dat, aes(x = forcats::fct_reorder(cat_lbl, pct), y = pct)) +
  geom_segment(aes(xend = cat_lbl, y = 0, yend = pct)) +
  geom_point(size = 2) +
  geom_text(aes(label = paste0(round(pct, 1), "%")),
            hjust = -0.2, size = 3) +
  scale_y_continuous(
    name   = "Anteil (%)",
    limits = c(0, 100),
    breaks = seq(0, 100, 10),
    expand = expansion(mult = c(0, 0.08))
  ) +
  geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
  coord_flip(clip = "off") +
  theme_minimal(base_size = 12) +
  theme(
    plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
    axis.text.y = element_text(lineheight = 0.9, size = 9),
    axis.title.x.top    = element_text(margin = margin(b = 8)),
    axis.ticks.x.top    = element_line()
  ) +
  labs(
    title    = "Umfang der Stelle – Anteil an allen Befragten",
    subtitle = paste0("Prozentbasis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
    x = NULL, y = "Anteil (%)"
  )

```

## Tätigkeitfeld

```{r}
#| label: taetigkeitsfeld
#| fig.height: 15
#| fig.width: 8
#| warning: false
#| message: false

# use long-format table (expects: ID, variable, category)
long_src <- if (exists("df_long")) df_long else if (exists("df_main")) df_main else NULL
stopifnot(!is.null(long_src), all(c("ID","variable","category") %in% names(long_src)))

var   <- "Tätigkeitsfeld"
n_obs <- n_distinct(long_src$ID)

dat <- long_src %>%
  filter(variable == var) %>%
  mutate(cat = stringr::str_squish(category)) %>%
  filter(!is.na(cat) & cat != "") %>%
  distinct(ID, cat) %>%                 # max 1 hit per Person × Kategorie
  count(cat, name = "n_cat", sort = TRUE) %>%
  mutate(
    pct     = 100 * n_cat / n_obs,
    cat_lbl = stringr::str_wrap(cat, 40)
  ) %>%
  arrange(pct)

ggplot(dat, aes(x = forcats::fct_reorder(cat_lbl, pct), y = pct)) +
  geom_segment(aes(xend = cat_lbl, y = 0, yend = pct)) +
  geom_point(size = 2) +
  geom_text(aes(label = paste0(round(pct, 1), "%")),
            hjust = -0.2, size = 3) +
  scale_y_continuous(
    name   = "Anteil (%)",
    limits = c(0, 100),
    breaks = seq(0, 100, 10),
    expand = expansion(mult = c(0, 0.08)),
    sec.axis = dup_axis(name = "Anteil (%)")
  ) +
  geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
  coord_flip(clip = "off") +
  theme_minimal(base_size = 12) +
  theme(
    plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
    axis.text.y = element_text(lineheight = 0.9, size = 9),
    axis.title.x.top    = element_text(margin = margin(b = 8)),
    axis.ticks.x.top    = element_line(),
    axis.title.x.bottom = element_text(margin = margin(t = 8))
  ) +
  labs(
    title    = "Tätigkeitsfeld – Anteil an allen Befragten",
    subtitle = paste0("Prozentbasis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
    x = NULL, y = "Anteil (%)"
  )

```

## Beschreibung der Aufgabe

```{r}
#| label: beschreibung_der_aufgabe
#| fig.height: 15
#| fig.width: 8
#| warning: false
#| message: false

# expects long table with: ID, variable, category
long_src <- if (exists("df_long")) df_long else if (exists("df_main")) df_main else NULL
stopifnot(!is.null(long_src), all(c("ID","variable","category") %in% names(long_src)))

var   <- "Beschreibung der Aufgabe"
n_obs <- n_distinct(long_src$ID)

dat <- long_src %>%
  filter(variable == var) %>%
  mutate(cat = stringr::str_squish(category)) %>%
  filter(!is.na(cat) & cat != "") %>%
  distinct(ID, cat) %>%                 # max 1 hit pro Person × Kategorie
  count(cat, name = "n_cat", sort = TRUE) %>%
  mutate(
    pct     = 100 * n_cat / n_obs,
    cat_lbl = stringr::str_wrap(cat, 40)
  ) %>%
  arrange(pct)

ggplot(dat, aes(x = forcats::fct_reorder(cat_lbl, pct), y = pct)) +
  geom_segment(aes(xend = cat_lbl, y = 0, yend = pct)) +
  geom_point(size = 2) +
  geom_text(aes(label = paste0(round(pct, 1), "%")),
            hjust = -0.2, size = 3) +
  scale_y_continuous(
    name   = "Anteil (%)",
    limits = c(0, 100),
    breaks = seq(0, 100, 10),
    expand = expansion(mult = c(0, 0.08)),
    sec.axis = dup_axis(name = "Anteil (%)")
  ) +
  geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
  coord_flip(clip = "off") +
  theme_minimal(base_size = 12) +
  theme(
    plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
    axis.text.y = element_text(lineheight = 0.9, size = 9),
    axis.title.x.top    = element_text(margin = margin(b = 8)),
    axis.ticks.x.top    = element_line(),
    axis.title.x.bottom = element_text(margin = margin(t = 8))
  ) +
  labs(
    title    = "Beschreibung der Aufgabe – Anteil an allen Befragten",
    subtitle = paste0("Prozentbasis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
    x = NULL, y = "Anteil (%)"
  )

```

## Persönliche Kompetenzen

```{r}
#| label: persoenliche_kompetenzen
#| fig.height: 5
#| fig.width: 8
#| warning: false
#| message: false

# expects long table with: ID, variable, category
long_src <- if (exists("df_long")) df_long else if (exists("df_main")) df_main else NULL
stopifnot(!is.null(long_src), all(c("ID","variable","category") %in% names(long_src)))

var   <- "Persönliche Kompetenzen"
n_obs <- n_distinct(long_src$ID)

dat <- long_src %>%
  filter(variable == var) %>%
  mutate(cat = stringr::str_squish(category)) %>%
  filter(!is.na(cat) & cat != "") %>%
  distinct(ID, cat) %>%                 # max 1 hit pro Person × Kategorie
  count(cat, name = "n_cat", sort = TRUE) %>%
  mutate(
    pct     = 100 * n_cat / n_obs,
    cat_lbl = stringr::str_wrap(cat, 40)
  ) %>%
  arrange(pct)

ggplot(dat, aes(x = forcats::fct_reorder(cat_lbl, pct), y = pct)) +
  geom_segment(aes(xend = cat_lbl, y = 0, yend = pct)) +
  geom_point(size = 2) +
  geom_text(aes(label = paste0(round(pct, 1), "%")),
            hjust = -0.2, size = 3) +
  scale_y_continuous(
    name   = "Anteil (%)",
    limits = c(0, 100),
    breaks = seq(0, 100, 10),
    expand = expansion(mult = c(0, 0.08))
  ) +
  geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
  coord_flip(clip = "off") +
  theme_minimal(base_size = 12) +
  theme(
    plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
    axis.text.y = element_text(lineheight = 0.9, size = 9),
    axis.title.x.top    = element_text(margin = margin(b = 8)),
    axis.ticks.x.top    = element_line()
  ) +
  labs(
    title    = "Persönliche Kompetenzen – Anteil an allen Befragten",
    subtitle = paste0("Prozentbasis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
    x = NULL, y = "Anteil (%)"
  )
```

## Sozial-kommunikative Kompetenzen

```{r}
#| label: sozial_kommunikative_kompetenzen
#| fig.width: 8
#| warning: false
#| message: false

# expects long table with: ID, variable, category
long_src <- if (exists("df_long")) df_long else if (exists("df_main")) df_main else NULL
stopifnot(!is.null(long_src), all(c("ID","variable","category") %in% names(long_src)))

var   <- "Sozial-kommunikative Kompetenzen"
n_obs <- n_distinct(long_src$ID)

dat <- long_src %>%
  filter(variable == var) %>%
  mutate(cat = stringr::str_squish(category)) %>%
  filter(!is.na(cat) & cat != "") %>%
  distinct(ID, cat) %>%                 # max 1 hit pro Person × Kategorie
  count(cat, name = "n_cat", sort = TRUE) %>%
  mutate(
    pct     = 100 * n_cat / n_obs,
    cat_lbl = stringr::str_wrap(cat, 40)
  ) %>%
  arrange(pct)

ggplot(dat, aes(x = forcats::fct_reorder(cat_lbl, pct), y = pct)) +
  geom_segment(aes(xend = cat_lbl, y = 0, yend = pct)) +
  geom_point(size = 2) +
  geom_text(aes(label = paste0(round(pct, 1), "%")),
            hjust = -0.2, size = 3) +
  scale_y_continuous(
    name   = "Anteil (%)",
    limits = c(0, 100),
    breaks = seq(0, 100, 10),
    expand = expansion(mult = c(0, 0.08))
  ) +
  geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
  coord_flip(clip = "off") +
  theme_minimal(base_size = 12) +
  theme(
    plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
    axis.text.y = element_text(lineheight = 0.9, size = 9),
    axis.title.x.top    = element_text(margin = margin(b = 8)),
    axis.ticks.x.top    = element_line()
  ) +
  labs(
    title    = "Sozial-kommunikative Kompetenzen – Anteil an allen Befragten",
    subtitle = paste0("Prozentbasis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
    x = NULL, y = "Anteil (%)"
  )
```

## Aktivitäts- und umsetzungsorientierte Kompetenzen

```{r}
#| label: aktivitaets_umsetzungsorientierte_kompetenzen
#| fig.height: 6
#| fig.width: 8
#| warning: false
#| message: false

# expects long table with: ID, variable, category
long_src <- if (exists("df_long")) df_long else if (exists("df_main")) df_main else NULL
stopifnot(!is.null(long_src), all(c("ID","variable","category") %in% names(long_src)))

var   <- "Aktivitäts- und umsetzungsorientierte Kompetenzen"
n_obs <- n_distinct(long_src$ID)

dat <- long_src %>%
  filter(variable == var) %>%
  mutate(cat = stringr::str_squish(category)) %>%
  filter(!is.na(cat) & cat != "") %>%
  distinct(ID, cat) %>%                 # max 1 hit pro Person × Kategorie
  count(cat, name = "n_cat", sort = TRUE) %>%
  mutate(
    pct     = 100 * n_cat / n_obs,
    cat_lbl = stringr::str_wrap(cat, 40)
  ) %>%
  arrange(pct)

ggplot(dat, aes(x = forcats::fct_reorder(cat_lbl, pct), y = pct)) +
  geom_segment(aes(xend = cat_lbl, y = 0, yend = pct)) +
  geom_point(size = 2) +
  geom_text(aes(label = paste0(round(pct, 1), "%")),
            hjust = -0.2, size = 3) +
  scale_y_continuous(
    name   = "Anteil (%)",
    limits = c(0, 100),
    breaks = seq(0, 100, 10),
    expand = expansion(mult = c(0, 0.08))
  ) +
  geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
  coord_flip(clip = "off") +
  theme_minimal(base_size = 12) +
  theme(
    plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
    axis.text.y = element_text(lineheight = 0.9, size = 9),
    axis.title.x.top    = element_text(margin = margin(b = 8)),
    axis.ticks.x.top    = element_line(),
    axis.title.x.bottom = element_text(margin = margin(t = 8))
  ) +
  labs(
    title    = "Aktivitäts- und umsetzungsorientierte Kompetenzen – Anteil an allen Befragten",
    subtitle = paste0("Prozentbasis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
    x = NULL, y = "Anteil (%)"
  )
```

## Denke an Deine bisherigen Teamerfahrungen zurück. Welche Rolle(n) nimmst Du in Teams am liebsten ein?

```{r}
#| label: teamrollen
#| fig.width: 8
#| warning: false
#| message: false

# expects long table with: ID, variable, category
long_src <- if (exists("df_long")) df_long else if (exists("df_main")) df_main else NULL
stopifnot(!is.null(long_src), all(c("ID","variable","category") %in% names(long_src)))

var_full <- "Denke an Deine bisherigen Teamerfahrungen zurück. Welche Rolle(n) nimmst Du in Teams am liebsten ein?"
n_obs    <- n_distinct(long_src$ID)

dat <- long_src %>%
  filter(variable == var_full) %>%
  mutate(
    cat = stringr::str_squish(category),
    # shorten category to the token BEFORE the first colon, also drop any leading "..." artifacts
    cat_short = cat %>%
      stringr::str_remove("^\\s*\\.\\.\\.") %>%
      sub(":.*$", "", .) %>%
      stringr::str_squish()
  ) %>%
  filter(!is.na(cat_short) & cat_short != "") %>%
  distinct(ID, cat_short) %>%          # max 1 hit pro Person × Kurz-Kategorie
  count(cat_short, name = "n_cat", sort = TRUE) %>%
  mutate(
    pct      = 100 * n_cat / n_obs,
    cat_lbl  = stringr::str_wrap(cat_short, 40)
  ) %>%
  arrange(pct)

ggplot(dat, aes(x = forcats::fct_reorder(cat_lbl, pct), y = pct)) +
  geom_segment(aes(xend = cat_lbl, y = 0, yend = pct)) +
  geom_point(size = 2) +
  geom_text(aes(label = paste0(round(pct, 1), "%")),
            hjust = -0.2, size = 3) +
  scale_y_continuous(
    name   = "Anteil (%)",
    limits = c(0, 100),
    breaks = seq(0, 100, 10),
    expand = expansion(mult = c(0, 0.08))
  ) +
  geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
  coord_flip(clip = "off") +
  theme_minimal(base_size = 12) +
  theme(
    plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
    axis.text.y = element_text(lineheight = 0.9, size = 9),
    axis.title.x.top    = element_text(margin = margin(b = 8)),
    axis.ticks.x.top    = element_line(),
    axis.title.x.bottom = element_text(margin = margin(t = 8))
  ) +
  labs(
    title    = "Teamrollen – Anteil an allen Befragten",
    subtitle = paste0("Prozentbasis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
    x = NULL, y = "Anteil (%)"
  )

```

## Welche Werte sind Dir in dem Team der zu besetzenden Stelle besonders wichtig?

```{r}
#| label: wichtige_werte_im_team
#| fig.height: 10
#| fig.width: 8
#| warning: false
#| message: false

# expects long table with: ID, variable, category
long_src <- if (exists("df_long")) df_long else if (exists("df_main")) df_main else NULL
stopifnot(!is.null(long_src), all(c("ID","variable","category") %in% names(long_src)))

var_full <- "Welche Werte sind Dir in dem Team der zu besetzenden Stelle besonders wichtig?"
n_obs    <- n_distinct(long_src$ID)

dat <- long_src %>%
  filter(variable == var_full) %>%
  mutate(cat = stringr::str_squish(category)) %>%
  filter(!is.na(cat) & cat != "") %>%
  distinct(ID, cat) %>%                 # max 1 hit pro Person × Kategorie
  count(cat, name = "n_cat", sort = TRUE) %>%
  mutate(
    pct     = 100 * n_cat / n_obs,
    cat_lbl = stringr::str_wrap(cat, 40)
  ) %>%
  arrange(pct)

ggplot(dat, aes(x = forcats::fct_reorder(cat_lbl, pct), y = pct)) +
  geom_segment(aes(xend = cat_lbl, y = 0, yend = pct)) +
  geom_point(size = 2) +
  geom_text(aes(label = paste0(round(pct, 1), "%")),
            hjust = -0.2, size = 3) +
  scale_y_continuous(
    name   = "Anteil (%)",
    limits = c(0, 100),
    breaks = seq(0, 100, 10),
    expand = expansion(mult = c(0, 0.08)),
    sec.axis = dup_axis(name = "Anteil (%)")
  ) +
  geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
  coord_flip(clip = "off") +
  theme_minimal(base_size = 12) +
  theme(
    plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
    axis.text.y = element_text(lineheight = 0.9, size = 9),
    axis.title.x.top    = element_text(margin = margin(b = 8)),
    axis.ticks.x.top    = element_line(),
    axis.title.x.bottom = element_text(margin = margin(t = 8))
  ) +
  labs(
    title    = "Wichtige Werte im Team – Anteil an allen Befragten",
    subtitle = paste0("Prozentbasis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
    x = NULL, y = "Anteil (%)"
  )
```

## Mit welchen Aussagen können Unternehmen bei Dir punkten?

```{r}
#| label: punkte_aussagen
#| fig.height: 9
#| fig.width: 9
#| warning: false
#| message: false

# expects long table with: ID, variable, category
long_src <- if (exists("df_long")) df_long else if (exists("df_main")) df_main else NULL
stopifnot(!is.null(long_src), all(c("ID","variable","category") %in% names(long_src)))

var_full <- "Mit welchen Aussagen können Unternehmen bei Dir punkten?"
n_obs    <- n_distinct(long_src$ID)

dat <- long_src %>%
  filter(variable == var_full) %>%
  mutate(cat = stringr::str_squish(category)) %>%
  filter(!is.na(cat) & cat != "") %>%
  distinct(ID, cat) %>%                 # max 1 hit pro Person × Kategorie
  count(cat, name = "n_cat", sort = TRUE) %>%
  mutate(
    pct       = 100 * n_cat / n_obs,
    # shorten very long statements just for labeling (keep full text in data)
    cat_lbl   = cat %>% stringr::str_wrap(50) %>% stringr::str_trunc(80)
  ) %>%
  arrange(pct)

ggplot(dat, aes(x = forcats::fct_reorder(cat_lbl, pct), y = pct)) +
  geom_segment(aes(xend = cat_lbl, y = 0, yend = pct)) +
  geom_point(size = 2) +
  geom_text(aes(label = paste0(round(pct, 1), "%")),
            hjust = -0.2, size = 3) +
  scale_y_continuous(
    name   = "Anteil (%)",
    limits = c(0, 100),
    breaks = seq(0, 100, 10),
    expand = expansion(mult = c(0, 0.08)),
    sec.axis = dup_axis(name = "Anteil (%)")
  ) +
  geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
  coord_flip(clip = "off") +
  theme_minimal(base_size = 12) +
  theme(
    plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
    axis.text.y = element_text(lineheight = 0.9, size = 9),
    axis.title.x.top    = element_text(margin = margin(b = 8)),
    axis.ticks.x.top    = element_line(),
    axis.title.x.bottom = element_text(margin = margin(t = 8))
  ) +
  labs(
    title    = "Aussagen – Anteil an allen Befragten",
    subtitle = paste0("Prozentbasis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
    x = NULL, y = "Anteil (%)"
  )
```

## Meine Bildungsabschlüsse

```{r}
#| label: meine_bildungsabschluesse
#| fig.height: 6
#| fig.width: 8
#| warning: false
#| message: false

var   <- "Meine Bildungsabschlüsse"

dat <- long_src %>%
  filter(variable == var) %>%
  mutate(cat = stringr::str_squish(category)) %>%
  filter(!is.na(cat) & cat != "") %>%
  distinct(ID, cat) %>%                 # max 1 hit pro Person × Kategorie
  count(cat, name = "n_cat", sort = TRUE) %>%
  mutate(
    pct     = 100 * n_cat / n_obs,
    cat_lbl = stringr::str_wrap(cat, 40)
  ) %>%
  arrange(pct)

ggplot(dat, aes(x = forcats::fct_reorder(cat_lbl, pct), y = pct)) +
  geom_segment(aes(xend = cat_lbl, y = 0, yend = pct)) +
  geom_point(size = 2) +
  geom_text(aes(label = paste0(round(pct, 1), "%")),
            hjust = -0.2, size = 3) +
  scale_y_continuous(
    name   = "Anteil (%)",
    limits = c(0, 100),
    breaks = seq(0, 100, 10),
    expand = expansion(mult = c(0, 0.08))
  ) +
  geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
  coord_flip(clip = "off") +
  theme_minimal(base_size = 12) +
  theme(
    plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
    axis.text.y = element_text(lineheight = 0.9, size = 9),
    axis.title.x.top    = element_text(margin = margin(b = 8)),
    axis.ticks.x.top    = element_line()
  ) +
  labs(
    title    = "Meine Bildungsabschlüsse – Anteil an allen Befragten",
    subtitle = paste0("Prozentbasis: alle Befragten (N = ", format(n_obs, big.mark = "."), ")"),
    x = NULL, y = "Anteil (%)"
  )
```

## Bruttojahresgehalt

```{r}
#| label: bruttojahresgehalt_long
#| fig.height: 8
#| fig.width: 9
#| warning: false
#| message: false

long_src <- if (exists("df_long")) df_long else if (exists("df_main")) df_main else NULL
stopifnot(!is.null(long_src), all(c("ID","variable","category") %in% names(long_src)))

var   <- "Bruttojahresgehalt"
n_obs <- dplyr::n_distinct(long_src$ID)

# exact order you showed (top to bottom = low → high)
bucket_order <- c(
  "Ich möchte dazu keine Angabe machen.",
  "unbezahltes Pflichtpraktikum",
  "bis 6.240 EUR",
  "bis 8.000 EUR",
  "bis 12.000 EUR",
  "bis zu 20.000 EUR",
  "20.000 - 30.000 EUR",
  "30.000 - 40.000 EUR",
  "40.000 - 50.000 EUR",
  "50.000 - 60.000 EUR",
  "60.000 - 70.000 EUR",
  "70.000 - 80.000 EUR",
  "80.000 - 90.000 EUR",
  "90.000 - 100.000 EUR",
  "100.000 - 110.000 EUR",
  "110.000 - 120.000 EUR",
  "120.000 - 130.000 EUR",
  "130.000 - 140.000 EUR",
  "140.000 - 150.000 EUR",
  "ab 150.000 EUR"
)

# toggle exclusions here if desired
exclude_buckets <- NULL

dat <- long_src %>%
  dplyr::filter(variable == var) %>%
  dplyr::transmute(
    ID,
    bucket = stringr::str_squish(category)
  ) %>%
  dplyr::filter(!is.na(bucket) & bucket != "") %>%
  dplyr::distinct(ID, bucket) %>%              # one bucket per person
  dplyr::mutate(bucket = factor(bucket, levels = bucket_order)) %>%
  dplyr::filter(!bucket %in% exclude_buckets) %>%
  dplyr::count(bucket, name = "n", drop = FALSE) %>%  # keep empty levels for clarity
  dplyr::mutate(
    pct      = 100 * n / n_obs,
    # label tweak only (do not alter 'bucket' itself)
    bucket_lab = dplyr::case_when(
      as.character(bucket) == "bis zu 20.000 EUR" ~ "bis 20.000 EUR",
      TRUE ~ as.character(bucket)
    )
  ) %>%
  dplyr::arrange(match(bucket, bucket_order))

# lollipop plot
ggplot(dat, aes(x = forcats::fct_reorder(bucket_lab, as.numeric(bucket)),
                y = pct)) +
  geom_segment(aes(xend = bucket_lab, y = 0, yend = pct)) +
  geom_point(size = 2) +
  geom_text(aes(label = paste0(round(pct, 1), "%")),
            hjust = -0.2, size = 3) +
  scale_y_continuous(
    name   = "Anteil (%)",
    limits = c(0, 100),
    breaks = seq(0, 100, 10),
    expand = expansion(mult = c(0, 0.08)),
    sec.axis = dup_axis(name = "Anteil (%)")
  ) +
  geom_hline(yintercept = 50, linetype = "dashed", linewidth = 0.4, color = "grey50") +
  coord_flip(clip = "off") +
  theme_minimal(base_size = 12) +
  theme(
    plot.margin = grid::unit(c(5.5, 30, 5.5, 5.5), "pt"),
    axis.text.y = element_text(lineheight = 0.9, size = 9),
    axis.title.x.top    = element_text(margin = margin(b = 8)),
    axis.ticks.x.top    = element_line(),
    axis.title.x.bottom = element_text(margin = margin(t = 8))
  ) +
  labs(
    title    = "Bruttojahresgehalt – Anteil an allen Befragten (Long-Daten)",
    subtitle = paste0("Prozentbasis: N = ", format(n_obs, big.mark = "."), 
                      if (length(exclude_buckets)) paste0(" | ohne: ", paste(exclude_buckets, collapse = ", "))),
    x = NULL, y = "Anteil (%)"
  )

```

## Co-occurrence: top pairs

```{r}
#| label: indicator-cooccurrence
#| tbl-cap: "Top co-occurring indicator pairs (support & percentage)"
if (length(ind_cols) > 1) {
  # binary matrix (NA -> 0)
  X <- as.matrix(df_main[ind_cols]); X[is.na(X)] <- 0L
  n <- nrow(X)

  # per-feature prevalence and 11-co-occurrence counts
  p    <- colSums(X) / n
  co11 <- t(X) %*% X

  lbl <- function(v) shorten_prefix(v) |> stringr::str_trunc(70)

  # build tidy table; keep each unordered pair only once (upper triangle)
  top_pairs <- as.data.frame(as.table(co11)) %>%
    rename(var1 = Var1, var2 = Var2, support_11 = Freq) %>%
    mutate(
      i1 = match(var1, colnames(co11)),
      i2 = match(var2, colnames(co11))
    ) %>%
    filter(i1 < i2, support_11 > 0) %>%      # <<< no duplicates
    mutate(
      pct_11 = round(100 * support_11 / n, 2)
    ) %>%
    transmute(
      `Feature A`      = lbl(as.character(var1)),
      `Feature B`      = lbl(as.character(var2)),
      `gemeinsame 1er` = as.integer(support_11),
      `Anteil (%)`     = pct_11
    ) %>%
    arrange(desc(`Anteil (%)`), desc(`gemeinsame 1er`)) %>%
    slice_head(n = 30)

  # print table
  if (requireNamespace("DT", quietly = TRUE)) {
    DT::datatable(
      top_pairs,
      options = list(pageLength = 15, scrollX = TRUE, dom = "tip"),
      rownames = FALSE
    )
  } else {
    knitr::kable(
      top_pairs,
      align = c("l","l","r","r"),
      caption = "Top co-occurring indicator pairs (höchster gemeinsamer Anteil)"
    )
  }
} else {
  cat("Not enough indicator columns for co-occurrence.\n")
}


```

## Response counts (how many indicators selected)

```{r}
#| label: burden
row_ones <- if (length(ind_cols)) rowSums(df_main[ind_cols], na.rm = TRUE) else rep(0, nrow(df_main))
ggplot(tibble(ones = row_ones), aes(x = ones)) +
  geom_histogram(bins = 30) +
  theme_minimal(base_size = 12) +
  labs(title = "Antwortumfang (Anzahl gesetzter Indikatoren pro Person)", x = "# Indikatoren", y = "Anzahl Personen")
```

```         
```

## Appendix exports

```{r}
#| label: appendix-exports
#| echo: false
#| message: false
#| warning: false

# ---- Full data dictionary (inside document) ----------------------------------
if (!exists("dict")) stop("`dict` not found — ensure the 'data-dictionary' chunk ran.")
dict_full <- dict %>%
  mutate(variable = shorten_prefix(variable)) %>%
  arrange(family, desc(n_unique))

if (requireNamespace("DT", quietly = TRUE)) {
  DT::datatable(
    dict_full,
    options = list(pageLength = 50, scrollX = TRUE),
    rownames = FALSE,
    caption  = "Full data dictionary (all columns)"
  )
} else {
  cat("### Full data dictionary (all columns)\n\n")
  print(dict_full, n = Inf)
}

# ---- Optional: show underlying summary tables (no saving) --------------------
if (exists("top_inds")) {
  cat("\n\n### Top indicator features (underlying table)\n\n")
  top_inds_out <- top_inds %>%
    mutate(
      feature = shorten_prefix(feature),
      share   = scales::percent(pct_ones, accuracy = 0.1)
    ) %>%
    select(Feature = feature, Selections = n_ones, Share = share)
  print(top_inds_out, n = nrow(top_inds_out))
}

if (exists("sc_missing")) {
  cat("\n\n### Single-choice with most missing / 'keine Angabe' (underlying table)\n\n")

  # Robustly compute 'Available (n)' even if source object lacks n_nonmissing
  sc_missing_out <- sc_missing %>%
    mutate(
      Variable = shorten_prefix(variable),
      `Missing share` = if ("pct_missing" %in% names(.)) {
        scales::percent(pct_missing / 100, accuracy = 0.1)
      } else {
        NA_character_
      },
      `Available (n)` = case_when(
        "n_nonmissing" %in% names(.) ~ n_nonmissing,
        exists("n_obs", inherits = TRUE) & "pct_missing" %in% names(.) ~
          as.integer(round(n_obs * (1 - pct_missing / 100))),
        TRUE ~ NA_integer_
      )
    ) %>%
    select(Variable, `Missing share`, `Available (n)`) %>%
    arrange(desc(`Available (n)`))

  print(sc_missing_out, n = nrow(sc_missing_out))
}

```

## Session info

```{r}
#| label: session
sessionInfo()
```
